---
title: "R Notebook"
output: html_notebook
---

Graficos das Corridas
Entrada de dados criar objeto corridas
```{r}
library(readxl)
form_corrida_para_r <- read_excel("form-corrida-para-r.xlsx")
corridas <- form_corrida_para_r
```
Colocar legendas e criar objeto corridas2
```{r}
library(expss)
corridas2 <- apply_labels(corridas,
                          idade= "Idade",
                          clasidade= "Classe Idade",
                          estadocivil= "Estado Civil",
                          emae="É Mãe?",
                          numfilhos= "Num Filhos",
                          tipoparto= "Tipo Parto",
                          teveepisotiomia= "Episotiomia",
                          cirurgiaginecologica= "CirurgiaG",
                          tipoativfisica= "AtivFisic",
                          freqsemcorr= "Freq Corr Sem",
                          clasfreqcor= "Cat Freq Corr",
                          anoscorrendo= "Corre Anos",
                          motivocorr= "Motiv Corr",
                          kmsemana= "Km Semana",
                          claskmsem= "Km Cat",
                          idadeiniciocorrida= "Idade Comecou",
                          vontadeurinarcorrida= "Vont Urinar",
                          perdaurinacorrida= "Perda Urina",
                          perdiantescorrer= "Perdia Antes",
                          quandoperdeurina= "Quando Perde")
```

Agora fazer uma tabela com os dados

```{r}
cro(corridas2$vontadeurinarcorrida,corridas2$perdaurinacorrida)
cro_tpct(corridas2$vontadeurinarcorrida,corridas2$perdaurinacorrida)
```

```{r}
corridas2 %>% 
  tab_cells(vontadeurinarcorrida) %>% 
  tab_cols(total(), perdaurinacorrida) %>% 
  tab_stat_cpct() %>% 
  tab_pivot()
```



Tentar o comando table

```{r}
compar1 <- table(corridas2$vontadeurinarcorrida,corridas2$perdaurinacorrida)
ftable(compar1)
summary(compar1)
```

Nova comparaćão perda de urina por classe de idade

```{r}
compar2 <- table(corridas2$clasidade,corridas2$perdaurinacorrida)
ftable(compar2)
summary(compar2)
```
Nova comparaćão perda de urina por distancia percorrida

```{r}
compar3 <- table(corridas2$claskmsem,corridas2$perdaurinacorrida)
ftable(compar3)
summary(compar3)
```
Mais uma comparacao perda de urina por freq corrida semanal

```{r}
compar4 <- table(corridas2$clasfreqcor,corridas2$perdaurinacorrida)
ftable(compar4)
summary(compar4)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
